### 2022-03-28 manuscript.tex
tuba [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/987c5d89817ca7e2654877bc3ecb872fb25a6d0f.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/987c5d89817ca7e2654877bc3ecb872fb25a6d0f/checks
https://github.com/scherzerthesis/thesis/actions/runs/2053775510

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/c38737afb577e35ec46750d76de1b28f67b86192/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/c38737afb577e35ec46750d76de1b28f67b86192}{scherzerthesis/thesis@c38737a}
on March 28, 2022.

@@

\begin{figure}
\hypertarget{fig:05}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba2.png}
\caption{**Figure 2.2. Jitter plot of calculated tumor cell number based on Tuba-Seq pipeline. Mean tumor number for 16 weeks \emph{Braf\textsuperscript{CAT/+}; H11b\textsuperscript{LSL-Cas9/+}} is 21,248 cells. Mean tumor number for 8 weeks \emph{Braf\textsuperscript{CAT/+}; H11b\textsuperscript{LSL-Cas9/+}} is 9,095 cells. Mean tumor number for 16 week \emph{Braf\textsuperscript{CAT/+}; H11b\textsuperscript{LSL-Cas9/+}} is 29,867 cells.}\label{fig:05}
}
\end{figure}

\begin{figure}
\hypertarget{fig:06}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba3.png}
\caption{\textbf{Figure 2.3. Jitter plot of calculated tumor cell number based on Tuba-Seq pipeline seperated by sgID. (A) 16 weeks \emph{Braf\textsuperscript{CAT/+}; H11b\textsuperscript{LSL-Cas9/+}}(negative control) has no apparent cooperative genetic events. (B)8 weeks \emph{Braf\textsuperscript{CAT/+}; H11b\textsuperscript{LSL-Cas9/+}} identifed Apc loss as a cooperating genetic event based on increase in tumor cell number (C) This is the title of Figure} this is the text.}\label{fig:06}
}
\end{figure}

\begin{figure}
\hypertarget{fig:07}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba4.png}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:07}
}
\end{figure}

\begin{figure}
\hypertarget{fig:08}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba5.png}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:08}
}
\end{figure}

\begin{figure}
\hypertarget{fig:09}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba6.png}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:09}
}
\end{figure}

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/987c5d89817ca7e2654877bc3ecb872fb25a6d0f/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/987c5d89817ca7e2654877bc3ecb872fb25a6d0f}{scherzerthesis/thesis@987c5d8}
on March 28, 2022.

@@

\begin{figure}
\hypertarget{fig:05}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba2.png}
\caption{**Figure 2.2. Jitter plot of calculated tumor cell number based on Tuba-Seq pipeline.Tumor size corresponds to dot size. Mean tumor number for 16 weeks \emph{Braf\textsuperscript{CAT/+}; H11b\textsuperscript{+/+}} is 21,248 cells. Mean tumor number for 8 weeks \emph{Braf\textsuperscript{CAT/+}; H11b\textsuperscript{LSL-Cas9/+}} is 9,095 cells. Mean tumor number for 16 week \emph{Braf\textsuperscript{CAT/+}; H11b\textsuperscript{LSL-Cas9/+}} is 29,867 cells.}\label{fig:05}
}
\end{figure}

\begin{figure}
\hypertarget{fig:06}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba3.png}
\caption{**Figure 2.3. Jitter plot of calculated tumor cell number based on Tuba-Seq pipeline seperated by sgID. (A) 16 weeks \emph{Braf\textsuperscript{CAT/+}; H11b\textsuperscript{+/+}}(negative control) has no apparent cooperative genetic events. (B) 8 weeks \emph{Braf\textsuperscript{CAT/+}; H11b\textsuperscript{LSL-Cas9/+}} identifed Apc loss as a cooperating genetic event based on increase in tumor cell number (C) 16 week \emph{Braf\textsuperscript{CAT/+}; H11b\textsuperscript{LSL-Cas9/+}} identified Apc and Setd2 loss as cooperating events.}\label{fig:06}
}
\end{figure}

\begin{figure}
\hypertarget{fig:07}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba4.png}
\caption{**Figure 2.4. Validation of \emph{Setd2} loss as cooperating genetic event in BRAF\textsuperscript{V600E} lung cancer. (A) Representative images of lung tumor histology of 16 weeks \emph{Braf\textsuperscript{CAT/+}; H11b\textsuperscript{LSL-Cas9/+}} mice infected with 2.5x10\textsuperscript{4} PFU Lenti-sgSetd2-Cre or Lenti-sgNT1-Cre. (B) Quantification of tumor size based on histology, n= 30 tumors. * = \_p-value\textless.05.}\label{fig:07}
}
\end{figure}

\begin{figure}
\hypertarget{fig:08}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba5.png}
\caption{**Figure 2.5. H3K36me\textsuperscript{3} is lost in larger tumors in \emph{Set2d}-edited lung tumors.(A) Representative images of H3K36me3 (surrogate for \emph{setd2} loss) depicting either ``high'' or ``low'' staining indicative of protein expression. (B) Quantification of H3K36me\textsuperscript{3} positive tumors in either \emph{sgSetd2} or \emph{sgNT1} targeted mice. \emph{= \emph{p-value\textless.05} for negative tumors. (C) Quantification of tumor size paired with H3K36me\textsuperscript{3} negative tumors. Tumor size and H3K36me\textsuperscript{3} positivty were simuletaneously measured using QuantCenter and binned in either ``low'' or ``High'' and then average tumor size was determined for each group. }= \emph{p-value\textless.05}.}\label{fig:08}
}
\end{figure}

\begin{figure}
\hypertarget{fig:09}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba6.png}
\caption{**Figure 2.6. \emph{SETD2} loss is common in human cancers, an indicator of poor prognosis and frequently occurs with \emph{BRAF\textsuperscript{V600E}} mutations. (A) Survival analysis with ``Survival'' R package indicates a trend towards poorer overall survival with low \emph{SETD2} mRNA in TGCA Lung adenocarcinoma dataset. (B) \emph{SETD2} mRNA is attenuated in Lung adenocarcinoma compared to normal lung tissue (C) \emph{SETD2} mutations significantly co-occur with BRAF\textsuperscript{V600E} mutations and are present in 40\% of \_BRAF\textsuperscript{V600E}) mutant Lung Adenocarcinoma.}\label{fig:09}
}
\end{figure}
